The Dark \LaTeX{} \\ \large An Example of the dndbook Class

### 2020-12-23 example.tex
Added an example of the DndMonster stat block formatted in vertical (single-column) layout
Tweaked the complex colour setting function to allow comment and sidebar to have different colours

@@

The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block

@@

>>>>

% Monster stat block
\begin{DndMonster}[float=t]{Monster Foo}
  \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}

  \begin{DndMonsterLegendaryActions}
    \DndMonsterLegendaryAction{Move}{The foo moves up to its speed.}
    \DndMonsterLegendaryAction{Dagger Attack}{The foo makes a dagger attack.}
    \DndMonsterLegendaryAction{Create Contract (Costs 3 Actions)}{The foo presents a contract in a language it knows and waves it in the face of a creature within 10 feet. The creature must make a DC 10 Intelligence saving throw. On a failure, the creature is incapacitated until the start of the foo's next turn. A creature who cannot read the language in which the contract is written has advantage on this saving throw.}
  \end{DndMonsterLegendaryActions}
\end{DndMonster}

@@

The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block.

The stat block can be formatted either as a single column, or as a block that spans the page horizontally.

@@

\subsection{Extra Theme Color Control}
Use |\DndSetComplexThemeColor| in order to have more precise control over the various theme colors defined within the document class. This command takes eight (8) |<color>| values that map to the following color variables within the theme:

\begin{DndTable}[header=Complex Theme Parameter Map]{clX}
  \textbf{\#} & \textbf{Variable Set} & \textbf{Affected Style} \\
  1 & \textit{themecolor} & Used in |DndSetThemeColor|; set for future compatibility \\
    & \textit{tablecolor} & |DndTable| \\
  2 & \textit{commentcolor} & |DndComment| \\
  3 & \textit{sidebarcolor} & |DndSidebar| \\
  4 & \textit{readaloudcolor} & |DndReadAloud| background \\
  5 & \textit{readaloudbordercolor} & |DndReadAloud| border \\
  6 & \textit{titlecolor} & Titles of sections (|section|, |subsection|, etc) \\
  7 & \textit{titlerulecolor} & |subsection| title ruling \\
  8 & \textit{pagecolor} & Page numbers and footer \\
\end{DndTable}

\begin{DndComment}{Note On Changing Schemes}
If a major color scheme change is attempted, it is
likely that the background ``paper'' (which can be overridden with
|\SetPaperImage|) and footerscroll.pdf will need
to be modified as well in order to fit the other color modifications.
\end{DndComment}

An example of these settings for a theme similar to the \textit{Ghosts of Saltmarsh} sourcebook. Note that the values for \textit{titlered} and \textit{titlegold} are used for the title and title rule colours unchanged in this example.

\begin{lstlisting}[basicstyle=\ttfamily\small]
\definecolor {mytheme} {HTML} {DCF1E5}
\definecolor {mycomment} {HTML} {E9F5F5}
\definecolor {mysidebar} {HTML} {E9F5F5}
\definecolor {myreadaloud} {HTML} {DCF1E5}
\definecolor {myreadaloudborder} {HTML} {8AA7A2}
\definecolor {mypagenum} {HTML} {B5D4CF}
\DndSetComplexThemeColor[mytheme][mycomment][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]
\end{lstlisting}
